White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-25 papers/wdmerger_II/paper.tex
Start writing up the AMR section

>>>>

Now we turn to an examination of the effect of spatial resolution on the detonation.
The first question we want to answer is: at reasonable uniform spatial resolution, is
the simulation converged when a detonation occurs? If the answer is no, then the
follow-up question is: can adaptive mesh refinement help achieve a converged simulation?

To answer these questions we performed a series of simulations at varying base
resolutions. In each case we ran the simulation to the point when the density
at the collision point reached $10^7\ \text{g / cm}^{-3}$, which we will informally
call the collision time, $t_{\rm c}$. The collision time is about $t_{\rm c} = 6.85\ \text{s}$
at high resolution. At low resolution, the simulation is slightly different because
of the distortion imposed by a rectangular grid representing initially spherical stars,
so the collision time is slightly later. Then, we restarted the run from this checkpoint
and reset the time to zero (such that $t_{\rm c} = 0$). The new simulation runs until about
$t = 2.15\ \text{s}$, so that the full 9 seconds are simulated. During this second phase
the detonation occurs. An estimate of the detonation time, $t_{\rm d}$, that serves well
is the time when the peak density on the grid first reaches $5 \times 10^9\ \text{K}$.
We measure the detonation time relative to $t_{\rm c}$. Approximately speaking, the later
$t_{\rm d}$ is, the more nickel is produced. As time passes, more white dwarf material
slams into the center, compressing and heating up the gas. Both effects are favorable
to production of nickel. So, a later $t_{\rm d}$ implies that more material can be converted
to nickel. Similarly, the speed of the detonation matters. A slower speed detonation prolongs
the collision event, allowing more gas to be processed into nickel.
